---
title: "PUC-SP Computing"
subtitle: "Module 04 -- R Markdown"
author: "Adriana Picoral"
date: "6/14/2021"
output:
  html_document:
    toc: true
    number_sections: true
---

```{r setup, include=FALSE}
library(knitr)
library(tidyverse)
opts_chunk$set(echo = FALSE, message = FALSE)
```

# Big title

You enter your text normally, and because it is not R, you won't get a parsing error. It will render as text. To do to italics *these words are in italics*. For bold, **these words are in bold**.

_italics_

__bold__

*This sentence is in italics __but I want some bold in there__*

## Second level title

I would enter my text here.

### Third level title

Reasons to learn R markdown:

* Separate semantics and formatting -- easier to change formatting
* Include R code into your prose -- reproducible research

I can create the same list, but ordered:

1. You don't have to keep track of numbers
1. Markdown generates the correct order for you
1. So you can add an item anywhere
1. When you change your data, all tables and plots update automatically -- just hit knit

> "Don't use Word, it breaks my heart" -- Adriana Picoral

# Emma book vs. script

## Read data in

Use shortcut *cmd/crtl + option/alt + i* to create a R code chunk.

```{r echo=TRUE}
annotated_tokens_emma <- read_tsv("processed-data/annotated-data.tsv")
```



```{r}
glimpse(annotated_tokens_emma)
```

## Subcorpora size

Here is the token count for each source (i.e., book vs. script).

```{r}
annotated_tokens_emma %>%
  count(source) %>%
  kable(col.names = c("Subcorpus", "Token Count"),
        caption = "Token count across subcorpora",
        format.args = list(big.mark = ","))
```

| Column One | Column 2 | Column 3 |
| ---------- | -------- | -------- |
| row 1 col 1 | row 1 col 2 | row 1 col 3 |
| row 2 col 1 | row 2 col 2 | row 2 col 3 |


| Subcorpus | Description |
| :--------- | :----------- |
| Book | all the words in the Emma novel |
| Script | all the words in the Emma (1996) movie script |

## Plots

Here's a plot with the top 15 most frequent tokens in each subcorpus.

```{r fig.height=3, fig.width=6, fig.align='center'}
library(tidytext)

annotated_tokens_emma %>%
  count(source, token) %>%
  group_by(source) %>%
  slice_max(order_by = n, n = 15) %>%
  ggplot(aes(x = n,
             y = reorder_within(token, n, source))) +
  geom_col() +
  facet_wrap(~source, scales = "free") +
  scale_y_reordered()
  

```



